---
title: "Introduction to Package Binomial"
author: "Madison Tagg"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to Binomial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>")
library(Workout03Binomial)
```


#Workout03 Binomial Package

###Binomial Distribution Purpose
    * The purpose of the creation of this R package is to implements functions for calculating probabilities of a Binomial Random Variable, and related calculations. In doing so, getting measurements and visualizations.

###Some Binomial Calculations:
1. bin_choose(n, k):
    * Description: calculates the number of combinations in which *k* successes can occur in *n* trials
    * Example:
```{r}    
bin_choose(n = 5, k = 2)
```
    
2. bin_probability(success, trials, prob):
    * Description: calculates the probability of getting *success* in *trials* assuming that the probability of success is *prob*.
    * Example:
```{r}
bin_probability(success = 2, trials = 5, prob = 0.5)
```

###Constructing a Binomial Distribution:
1. bin_distribution():
    * Description: creates a data frame with the probaility distribution with *success* in the first column, and *probability* in the second column.
    * Example:
```{r}
bin_distribution(trials = 5, prob = 0.5)
```
    * *Plotting the Binomial Distribution* with the function plot()
```{r}
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)
```

2. bin_cumulative():
    * Description: creates a data frame with the probaility distribution with *success* in the first column, and *probability* in the second column, and cumlative probability in the third column.
    * Example:
```{r}
bin_cumulative(trials = 5, prob = 0.5)
```
    * *Plotting the Binomial Distribution* with the function plot()
```{r}
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)
```

###Calculating a Binomial Summary:
1. bin_variable(trials, p):
    * Description: prints out the binomial variable
    * Example:
```{r}
bin_variable(trials = 10, p = 0.3)
```

2. summary():
    * Description: Using the bin_variable that you constructed, one can calculate the summary of the binomial variable by using this function.
    * Example:
```{r}
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

### More Functions of measures:
    * Description: This package contains more main functions and one can see how invoke these functions below in the table:

*Table: Measurement Functions*


Measures:      | Functions to Use:          |  Example:
---------------|----------------------------|-----------------------------
mean           | bin_mean(trials,prob)      | bin_mean(4, 0.25) = 1
variance       | bin_variance(trials,prob)  | bin_variance(4, 0.25) = 0.75
mode           | bin_mode(trials,prob)      | bin_mode(4, 0.25) = 1
skewness       | bin_skewness(trials,prob)  | bin_skewness(4, 0.25) = 0.58
kurtosis       | bin_kurtosis(trials,prob)  | bin_kurtosis(4, 0.25) = -0.16





